\input{include/preamble.tex}
\title{Disposition 11: State Machine Replication}   
\author{Mathias Ravn Tversted} 
\date{\today} 


%===================================

% What is a state machine

% What is a replicated state machine
    % Replicated on several servers: Why does it have to be a state machine?

% Keeping consistency
% Solution: Totally-ordered broadcast

% Totally-ordered broadcast
    % What is it?
    % EITHER
        % Synchronous implementation: Round robin sequencer
        % Asynchronous implementation: Fig 11.4. Core-set selection. Large common subsets of inputs, async BA to nail down core set

% Client-centric consistency
    % What and how?



\begin{document}

\frame{\titlepage} 

\frame{\frametitle{Table of contents}\tableofcontents} 


%===================================
\section{State machine}
        \begin{frame}
            \frametitle{Definition of a state machine}
                A state machine consists of 
                \begin{itemize}
                    \item A set of states
                    \item Initial state $State_0 \in States$
                    \item Set of $Inputs$
                    \item Set of $Outputs$
                    \item Transition function $T: States \times Inputs \rightarrow States \times Outputs$
                \end{itemize}
        \end{frame}
%===================================
\section{Replicated state machine}
        \begin{frame}
            \frametitle{IF and definition of Replicated State Machine}
                We have I/O ports $RSM_i$ and the following ports
                \begin{itemize}
                    \item $\forall i Received_i$ outputs what IF has Received
                    \item $Process$ says what should be processed next
                    \item $Deliver_i$ instructs IF to deliver the next message to $S_i$
                \end{itemize}
                It has the following safety requirements:
                    \begin{itemize}
                        \item \textbf{Validity}: If honest server outputs $(y_i, ..., y_n)$ Then $\exists (x_1, ..., x_n) : (y_1, ..., y_n) = M(x_1, ..., x_n)$
                        \item \textbf{Agreement}: If honest server outputs $(y_1, ... y_n)$ then all other servers output at least some prefix of that, or vice versa
                    \end{itemize}
        \end{frame}
    \begin{frame}
        \frametitle{Ideal Functionality of an RSM}
            \begin{itemize}
                \item Let $State = State_0$. Foreach $RSM_i$, $Q_i = \emptyset$. 
                \item $Q_i$ is the outputs for $S_i$, which has not yet been delivered. Let $UnProcessed = \emptyset$
                \item On input x to $RSM_i$, output x on $Received_i$, add x to $UnProcessed$
                \item On input x on $Process$. If $x \in Unprocessed$, compute $(State', y) = T(state, x)$. Add $y$ to $Q_i$. Pop x from $UnProcessed$
                \item On input $Deliver_i$, where $Q_i \neq \emptyset$, remove first $y_i \in Q_i$ and output $y$ on $RSM_i$
            \end{itemize}
    \end{frame}
%===================================
\section{Consistency: TOB}
    \begin{frame}
        \frametitle{Consistency}
            In order to keep everyone consistent, we need to build it on \textit{Total-Ordered Broadcast}. Because we have state machines, the order of processing matters, therefore we need to be able to have all the machines process things in the same order.
            These can be 
            \begin{itemize}
                \item Synchronous TOB
                \item Async TOB
                \item Eventually synchronous broadcast
            \end{itemize}
    \end{frame}
    \subsection{Synchronous implementation}
        \begin{frame}
            \frametitle{Synchronous Implementation of TOB}
                \begin{itemize}
                    \item On x at $S_i$, flood it 
                    \item All servers $S_i$ keep $UnQueued_i$ of received messages. These could be received in arbitrary order
                    \item All servers $S_i$ keep a set $Queued_i$. When they move messages from $UnQueued$ to $Queued$, they do so in the same order
                    \item There is a leader $L$ (sequencer), who makes the order. Corrupted leader may break liveness but not safety
                    \item If a message is put into $Queued$, they do it in the same order. Leadership goes round-robin. This guarantees liveness
                    \item This happens with blocks
                \end{itemize}
        \end{frame}

    \subsection{Async implementation}
        \subsubsection{Enten den her}
            \begin{frame}
                \frametitle{Adapting IF to Async broadcast}
                    Now we have a notion of an epoch, $Unqueued$ and we transmit multiple inputs in combined blocks. 
                    \begin{enumerate}
                        \item On input x to TOB, add it to $Unqueued$
                        \item Leader of epoch is $P_i \mod n$ 
                        \item Leader adds $Unqueued$ to block and broadcasts it
                        \item When receiving block, add it to $Q$
                    \end{enumerate}
            \end{frame}
        \subsubsection{Eller den her}
            \begin{frame}
                \frametitle{Core-set selection: EKSTRA STUFF DER KAN SPRINGES OVER?}
                    We cannot reliably wait for the leader in each epoch. So we have everyone propose a block, and when a block is \textit{seen by many honest}, we can trust it. We simply have everyone collect these blocks and take the union of them. We have Byzantine Agreement available to us in the async model. 
            \end{frame}
            \begin{frame}
                \frametitle{Tidsmæssigt problematisk: Core-set selection}
                    Per fig. 11.4
                
            \end{frame}

%===================================
\section{Client-centric consistency}
    \begin{frame}
        \frametitle{Client vs. Server side consistency}
        \textbf{Server-side}, which is all honest servers executing commands in the same order
        
        \textbf{Client-side}, which is servers being behind other servers. This is why agree requires that for honest servers, that their output is a prefix of another honest parties output
    \end{frame}



\end{document}

