\input{include/preamble.tex}
\newcommand{\N}{\mathbb{N}}

\title{Disposition 7: Consistency}   
\author{Mathias Ravn Tversted} 
\date{\today} 


%===================================
\begin{document}
\frame{\titlepage} 

\frame{\frametitle{Table of contents}\tableofcontents} 


%===================================
% Unstructured P2P as motivation (messages arrive in different order)

% Consistency models and how to implement them
    % Model: Safety property phrased abstractly
    % Implementation: How to implement it

% FIFO

% Causal 
    % Causal-past relation
    % How to implement with vector clocks

% Total order
    % What how

%===================================
\section{Unstructured Peer to Peer}
    \begin{frame}
        \frametitle{Flooding Network}
            A flooding network is a network where messages are flooded. This guarantees that if a message is sent, it will eventually be delivered to all correct processes. When receiving a new message, it is simply sent to all other peers. This means that we cannot guarantee total ordering since messages can overtake each other. 
    \end{frame}


%===================================
\section{Consistency models}
%===================================
\section{FIFO}
    \begin{frame}
        \frametitle{First In, First Out (FIFO)}
            We want to preserve the order of communications. We can do this through FIFO (First In, First Out). 
            \textbf{FIFO}: If a correct $P_i$ sends $(P_i, m)$ and later sends $(P_i, m')$ then it holds for all correct $P_j$ that if they deliver $(P_i, m')$, then they delivered $(P_i, m)$ earlier. 
            User Contract and Liveness is the same as for \textit{Flood}. 
    \end{frame}
    \begin{frame}
        \frametitle{FLOOD2FIFO: This Time It's Protocol}
            \begin{itemize}
                \item Each party $P_i$ sets counter $c_i = 0$. This counts number of \textit{messages sent}
                \item Initialise $n$ counters $r_{i, j} = 0$ for $j = 1, ..., n$ These track how many messages $P_i$ received from $P_j$
                \item $P_i$: When sending message $m$, let $c_i = c_i + 1$. Send $P_i, c_i, m$ on floodin network. So tag each message with seq number.
                \item $P_i$. When receiving $(P_j, c, m)$ store it in buffer until $r_{i, j} = c + 1$. Now let $r_{i, j} = r_{i, j} + 1$ and output $(P_j, m)$. Since $r_{i, j}$ is the number of messages $P_i$ received from $P_j$, if $r_{i, j} = c + 1$ then $(P_j, c, m)$ is the next message. 
            \end{itemize}
    \end{frame}


%===================================
\section{Casuality}
    \begin{frame}
        \frametitle{Causuality}
            Just because messages arrive in FIFO order, does not mean that this is a meaningful order. \textit{Casual order} looks at which messages could have \textit{caused} other messages. This could be things such as messages in a messaging application. To fix this, we send the \textit{casual past} of messages with it. This is the set of messages that could have influenced the message that we sent. 

    \end{frame}

    \begin{frame}
        \frametitle{Causal-Past Relation}
            There is a notion that certain messages could have \textit{caused} other messages. Or "the happens-before relation". 

            \textbf{Kasusel-past relation}: $(P_i, m_i) \hookrightarrow (P_j, m_j)$
        
            If there is a chance that $m_j$ depends on $m_i$, then we treat it as if that is the case. 

            Denote $CasualPast(P_j, m) = \{(P_i, m_i) | (P_i, m_i) \hookrightarrow (P_j, m_j) \}$ the set of things that may depend on $(P_i, m_i)$. 

            We can similarly define a \textit{Kausual Future}. 
    \end{frame}

    \begin{frame}
        \frametitle{Casual-Past Relation}
            Sending the entire set of messages that we have received along with a message is a lot of data. Instead of this, we will use vector clocks.
    \end{frame}

    \begin{frame}
        \frametitle{Vector Clocks}
            For a system of $n$ parties, a \textit{vector clock} is a vector $VectorClock \in \N^n$ where $VectorClock[P_j] \in \N$ where that is the entry associated with party $P_j$. Since each party has a vector clock, VectorClock($P_i$) is the vector clock of $P_i$.
            $VectorClock(P_i)[P_j] = s$ means that $P_i$ knows that $P_j$ has sent $s$ messages. 
            \begin{itemize}
                \item When $P_i$ sends message $m$ it increments $VectorClock(P_i)[P_i]$ by one
                \item When $P_i$ sends message $m$ it sends along $VectorClock(P_i)$. When $P_i$ sends $m$ that message can be influenced by exactly the messages that have influenced $P_i$ at the time $P_i$ sends a message. 
            \end{itemize}
    \end{frame}
    \begin{frame}
        \frametitle{Vector Clocks}
            \begin{itemize}
                \item By sending the vector clock with the message, you can determine which messages could have influenced $m$
                \item Formally: $s = VectorClock(P_i, m)[P_j]$ messages from $P_j$ could have influenced $m$
            \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{Vector Clocks}
            \begin{itemize}
                \item Any receiver $P_r$ knows that it is safe to deliver $(P_i, m)$ once it delivered $s$ messages from $P_j$ it is $s$ that could have influenced $m$
                \item To keep track of how many messages were delivered from each party $P_j$ keeps a vector clock $Delivered(P_j)$, where $Delivered(P_j)[P_i]$ is how manymessages $P_j$ delivered from $P_i$. This gives the rule that $P_j$ can deliver $(P_i, m)$ once it holds for all $P_k$ that $Delivered(P_j)[P_k] \geq VectorClock(P_i, m)[P_k]$
            \end{itemize}
    \end{frame}


    \begin{frame}
        \frametitle{C-ass-ual network: In Practice}
            \begin{itemize}
                \item \textbf{Ports}: It connects $n$ parties. For each party there is a port $Casuel_i$. It has ports leak and deliver
                \item \textbf{Init}: $\forall P_i$ keep $Delivered_i = Sent = \emptyset$
                \item \textbf{Send}: On input $(P_i, m)$ on $Kasusel_i$. $Sent = Sent \cup (P_i, m)$. $KasuselPast(P_i, m) = CasualPast(P_i) \cup (P_i, m)$
                \item On $(P_j, P_i, m)$ where $(P_j, m) \in Sent$ but not Delivered. If $KasuselPast(P_j, m) \subset Delivered_i \cup (P_j, m)$ then deliver it and update Kasualpast. 
            \end{itemize}
    \end{frame}

%===================================
\section{Total order}
    \begin{frame}
        \frametitle{Total Order}
            \textbf{Total Order}: If correct $P_k$ delivered $(P_i, m)$ and later delivered $(P_j, m')$. Then it holds for all $P_m$ that if they deliver $(P_j, m')$ they delivered $(P_i, m)$ earlier. 
        
            We can implement this using Kasusel ordering and Vector Clocks. 
    \end{frame}

        \begin{frame}
            \frametitle{TOB from Casuselss and shizzle}
                We do this by achieving causual order, and then using a deterministic method for determining the order of concurrent messages. Such as lexocographically. 
        \end{frame}

\end{document}

